Fusion Moves for Correlation Clustering

### 2014-10-24 paper/alg_graph.tex
minor changes

    \draw node[opBox] (gen) {GENERATOR};
    \draw node[cutNode,right = 1cm of gen] (proposal_cut) {$\bar{P}$};
    \draw node[right of = proposal_cut](dummy){};
    \draw node[cutNode,right of = dummy] (best_cut) {$P$};
    \draw node[opBox,below of = dummy] (intersect) {INTERSECT\\UNCUT};
    \draw node[cutNode,below of = intersect] (int_cut){$\tilde{P}$};
    \draw node[opBox,below of = int_cut] (contract) {CONTRACT\\UNCUT\\EDGES};
    \draw node[gNode,right = 2cm of contract](cgraph)  {$( \tilde{\mathcal{G}}, \tilde{\mathcal{W}})$};
    \draw node[opBox, above of =  cgraph] (multicut) {MULTICUT};
    \draw node[cutNode,above of = multicut] (rcut) {$\bar{P}^{\tilde{\mathcal{G}}}$};
    \draw node[opBox, above of =  rcut] (pback) {PROJECT\\CUT\\BACK};

@@

    \draw node[gNode,below = of gen](graph)  {$( \mathcal{G}, \mathcal{W})$};
    \path[]
    (gen) edge[aEdge]  node[]{} (proposal_cut)
    (graph) edge[aEdge] (gen)
    (proposal_cut)  edge[aEdge]   (intersect)
    (best_cut)      edge[aEdge]   (intersect)
    (intersect)     edge[aEdge]   (int_cut)
    (int_cut)       edge[aEdge]   (contract) 
    (contract)      edge[aEdge,above]   
        node[edgeLabelNode]{coarse graphs\\with fewer nodes}(cgraph)
    (cgraph)        edge[aEdge]   (multicut)
    (multicut)      edge[aEdge]   (rcut)
    (rcut)          edge[aEdge]   (pback)
    (pback)         edge[aEdge]   (best_cut)
    (graph)         edge[aEdge]   (contract.west)
    (best_cut)      edge[aEdge,dashed,bend angle=90,bend right,draw=gray!30]  
        node[edgeLabelNode]{current best solution\\can influence generator}  (gen)
    ;
\end{tikzpicture}
\caption{
    The proposed algorithm works in the following way:
    Given a graph $\mathcal{G}$, edge weights $\mathcal{W}$ and
    a proposal generator, the current best solution $P$ is iteratively improved.
    A proposal generator generates different versatile
    proposal partitions $\bar{P}$.
    The proposal  $\bar{P}$ is intersected with $P$ which results in
    $\tilde{P}$. Contracting each each which is not 
    cut in $\tilde{P}$ leads to a coarser graph  
    $\tilde{\mathcal{G}} = ( \tilde{\mathcal{V}}, \tilde{\mathcal{E}} )$ 
    with new edge weights $\tilde{\mathcal{W}}$.
    If  $\bar{P}$ and $P$ have a small fraction of cut edges, $\tilde{\mathcal{G}}$ will be small ( $|\tilde{\mathcal{V}}| << |\mathcal{V}|$
    and $|\tilde{\mathcal{E}}| << |\mathcal{E}|$).
    The multicut objective on the smaller graph $\tilde{\mathcal{G}}$ can be optimized magnitudes 
    faster than on $\tilde{\mathcal{G}}$.
    It is guaranteed that the optimal multicut partitioning $\bar{P}^{\tilde{\mathcal{G}}}$ on $\tilde{\mathcal{G}}$ projected 
    back to $\mathcal{G}$ as a lower or equal energy than any of the two input partitions $P$ and $\bar{P}$, 
    therefore we store the result of fusion as new best state $P$ and repeat the procedure.
}\label{fig:algo_graph}
\end{figure}

>>>>

    \draw node[opBox] (gen) {GENERATOR};
    \draw node[cutNode,right = 1cm of gen] (proposal_cut) {$\bar{y}$};
    \draw node[right of = proposal_cut](dummy){};
    \draw node[cutNode,right of = dummy] (best_cut) {$y$};
    \draw node[opBox,below of = dummy] (intersect) {INTERSECT\\UNCUT};
    \draw node[cutNode,below of = intersect] (int_cut){$\tilde{y}$};
    \draw node[opBox,below of = int_cut] (contract) {CONTRACT\\UNCUT\\EDGES};
    \draw node[gNode,right = 2cm of contract](cgraph)  {$( \tilde{\mathcal{G}}, \tilde{\mathcal{w}})$};
    \draw node[opBox, above of =  cgraph] (multicut) {MULTICUT};
    \draw node[cutNode,above of = multicut] (rcut) {$\bar{w}^{\tilde{\mathcal{G}}}$};
    \draw node[opBox, above of =  rcut] (pback) {PROJECT\\CUT\\BACK};

@@

    \draw node[gNode,below = of gen](graph)  {$( \mathcal{G}, \mathcal{w})$};
    \path[]
    (gen) edge[aEdge]  node[]{} (proposal_cut)
    (graph) edge[aEdge] (gen)
    (proposal_cut)  edge[aEdge]   (intersect)
    (best_cut)      edge[aEdge]   (intersect)
    (intersect)     edge[aEdge]   (int_cut)
    (int_cut)       edge[aEdge]   (contract) 
    (contract)      edge[aEdge,above]   
        node[edgeLabelNode]{coarse graphs\\with fewer nodes}(cgraph)
    (cgraph)        edge[aEdge]   (multicut)
    (multicut)      edge[aEdge]   (rcut)
    (rcut)          edge[aEdge]   (pback)
    (pback)         edge[aEdge]   (best_cut)
    (graph)         edge[aEdge]   (contract.west)
    (best_cut)      edge[aEdge,dashed,bend angle=90,bend right,draw=gray!30]  
        node[edgeLabelNode]{current best solution\\can influence generator}  (gen)
    ;
\end{tikzpicture}
\caption{
    The proposed algorithm works in the following way:
    Given a graph $\mathcal{G}$, edge weights $\mathcal{w}$ and
    a proposal generator, the current best solution $y$ is iteratively improved.
    A proposal generator generates different versatile
    proposal partitions $\bar{y}$.
    The proposal  $\bar{y}$ is intersected with $y$ which results in
    $\tilde{y}$. Contracting each each which is not 
    cut in $\tilde{y}$ leads to a coarser graph  
    $\tilde{\mathcal{G}} = ( \tilde{\mathcal{V}}, \tilde{\mathcal{E}} )$ 
    with new edge weights $\tilde{\mathcal{w}}$.
    If  $\bar{y}$ and $y$ have a small fraction of cut edges, $\tilde{\mathcal{G}}$ will be small ( $|\tilde{\mathcal{V}}| << |\mathcal{V}|$
    and $|\tilde{\mathcal{E}}| << |\mathcal{E}|$).
    The multicut objective on the smaller graph $\tilde{\mathcal{G}}$ can be optimized magnitudes 
    faster than on $\tilde{\mathcal{G}}$.
    It is guaranteed that the optimal multicut partitioning $\bar{y}^{\tilde{\mathcal{G}}}$ on $\tilde{\mathcal{G}}$ projected 
    back to $\mathcal{G}$ as a lower or equal energy than any of the two input partitions $y$ and $\bar{y}$, 
    therefore we store the result of fusion as new best state $y$ and repeat the procedure.
}\label{fig:algo_graph}
\end{figure}

### 2014-10-24 paper/egpaper_for_review.tex
minor changes

\subsection{Problem Formulation}
\begin{center}
    \begin{eqnarray}
        l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
        y_{ij}^* &=& [l_{u} \neq l_{v}]  
    \end{eqnarray}
\end{center}

Problem-> Ambiguity

@@

\subsection{Related Work}

@@

\subsubsection{Correlation Clustering}
   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

\subsubsection{Fusion Moves}
Move making algorithms, in particular fusion moves, 
have become increasingly popular for energy minimization~\cite{???,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.

>>>>

\section{Problem Formulation}
Def: Graph, weighted graph, cut, multicut

\begin{center}
    \begin{eqnarray}
        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \label{eq:nodeproblem}\\
   %     y_{ij}^* &=& [l_{u} \neq l_{v}] 
        y^* &=& \argmin_{y \in MC(G)\cap \{0,1\}^{|E|}} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
    \end{eqnarray}
\end{center}

The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
Consequently, 
(i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
and (ii) the node-labeling is not unique for a given partitioning and introduce some
ambiguities.

@@

\section{Related Work}

@@

\subsection{Correlation Clustering}
   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

\subsection{Fusion Moves}
Move making algorithms, in particular fusion moves, 
have become increasingly popular for energy minimization~\cite{???,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.
